Strotor: A Minimalistic Approach to \\ Exploring Hierarchical Data

### 2014-04-15 paper/paper.tex
...

@@

\begin{document}
\title{Strotor: A Minimalistic Approach to \\
Exploring Large Hierarchical Data}
\author{
\begin{tabular}{l}
\parbox{5.5cm}{
\begin{center}
Toshiyuki Masui\\
Keio University\\
masui@pitecan.com
~ \\
~ \\
~
\end{center}
}
\end{tabular}
}
\maketitle
\abstract
We introduce a new simple information navigation technique
that enables users to explore large hierarchical data structure
using only two keys or one rotating device that can generate
two different signals based on the rotation direction.
%
Using the disk-based system called "Strotor",
users can find an entry in a huge hierarchical database easily
only by rotating a disk or a cylinder in two directions.
%
Strotor can be easily installed in sofas, kitchens, cars, etc.
where standard keyboards and remote controllers do not fit.

@@

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using only 2 keys.
In that case, we can use a rotating device like a disk or a cylinder for the navigation,
since the device can generate two key signals based on the direction of the rotation.
%
% We have developed a new navigation technique where only two keys are required
% for exploring large hierarchical data, and implemented the system on
% a rotating device ``Strotor''.
%
We have developed a new navigation technique and device called ``Strotor'',
where users can explore large hierarchical database by simple rotating operation.

@@

Stroter's behavior is based on the following simple principles.
Two types of input, ``U'' (up) and ``D'' (down), are used for the navigation.
They can be generated either by rotating the Strotor device or typing a keyboard.

\begin{enumerate}
\item A portion of a hierarchical data is shown to the user.

\item Always one element in the hierarchical data is selected and highlighted.

@@

\item Users can generate U to select the new element above the currently selected element,
and generate D to select the new element below the selected element.
Whenever the selection is changed, 3. is performed.
If the depth of the newly selected element is different from the currently
selected element, siblings of the currently selected element will disappear.

\item When a newly selected element has children and the user does no further operations,
the first child of the selected elemented is selected, and 3. is performed.
As a result, all the siblings of the newly selected element
(the first child of the currently selected elmeent) appear in the list.

@@

We show how Strotor works, using a hierarchical data structure of
shops list in a shopping mall shown in Figure \ref{fig1}.
Rectangles with thick border represent categories, and
other rectangles represent individual shops.

@@

When the user generates D twice and stops the operation,
\tsf{Fresh grocery} category is selected (Figure \ref{fig6}), and
after a short moment,
the shops under the category is automatically selected (Figure \ref{fig7}).

@@

@@

When the user generates U here, \tsf{Fresh grocery} is selected,
the shops under \tsf{Fresh grocery} disappears (Figure \ref{fig6}).
If the user generates U two more times, the display changes to the state
shown in Figure \ref{fig5},
and one more U will yield Figure \ref{fig4}.

@@

When the user generates D twice in Figure \ref{fig7},
\tsf{Clothing} is selected, and the display changes to Figure \ref{fig8}.

@@

A prototype system was built in JavaScript and the system runs on modern browsers.
Huge list of of news articles, movies, anime films, musics, and e-books are listed in one browser window
and the content is displayed in another window.
Users can hit two arrow keys or use the PowerMate device for the navigation.

\begin{figure}[H]
\centerline{\includegraphics[width=50mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
\caption{PowerMate device used for the Strotor prototype.}
\label{powermate}
\end{figure}

@@

4-way navigation are quite common for exploring hierarchical data structure,
and modern computer users have no problem using it.
Many mobile phones and PDAs are equipped with a jog dial with a push button,
where the dial is used for selecting an item from a list and 
the push button is used for moving to the next level.
PowerMate is equipped with a push button which can used for such purposes.
% As far as we know,
To the best of the authors' knowledge,
Strotor is the only interaction method for exploring hierarchical data structure
with one rotating device.

Using a conventional hierarchical menu, children elements are displayed automatically
when the parent element is selected by a mouse.
The ``automatic expansion'' feature is Strotorと同じ。

@@

LensBar\cite{Masui:1998:LVB:647341.721215}
is also a ZUI system for handling large hierarchical data,
but the same data structure used in LensBar can be used for Strotor.
Users can use a pointing devices when it is appropriate,
and use two keys or a disk device when pointing devices is not available.

@@

No formal evaluation have been done yet, but Strotor has been used in the authors'
living room for several months, and the author's family members are using it
everyday for watching anime films and listening to music.

Since the only thing a user can do with Strotor is rotating the device,
a user can use the device and see what happens without thinking about
other interactions.
Using a disk device for data navigation might be a new experience for
most of the users, but the hard restriction of the usage seems to be a
good thing.

>>>>

\long\def\ST{\textsf{\small{Strotor}}}

@@

\begin{document}
\title{Strotor: A Minimalistic Approach to \\
Exploring Hierarchical Data}
\author{
\begin{tabular}{l}
\parbox{5.5cm}{
\begin{center}
Toshiyuki Masui\\
Keio University\\
masui@pitecan.com
~ \\
~ \\
~
\end{center}
}
\end{tabular}
}
\maketitle
\abstract
We introduce a new simple information navigation technique
that enables users to explore large hierarchical data structure
using only two keys or one rotating device that can generate
two different signals based on the rotation direction.
%
Using the rotation-based input device called ``\ST'',
users can find an entry in a huge hierarchical database easily
only by rotating a disk or a cylinder in two directions.
%
{\ST} can be easily installed in sofas, kitchens, cars, etc.
where standard keyboards and remote controllers do not fit.

@@

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using only 2 keys.
In that case, we can use a rotating device like a disk or a cylinder for the navigation,
since the device can generate two key signals based on the direction of the rotation.
%
% We have developed a new navigation technique where only two keys are required
% for exploring large hierarchical data, and implemented the system on
% a rotating device ``Strotor''.
%
We have developed a new navigation technique and device called ``{\ST}'',
where users can explore large hierarchical database by simple rotating operation.

@@

{\ST}'s behavior is based on the following simple principles.
Two types of input, ``U'' (up) and ``D'' (down), are used for the navigation.
They can be generated either by rotating the {\ST} device or typing a keyboard.

\begin{enumerate}
\item A portion of the data is shown to the user as a list.

\item Always one element in the list is selected and highlighted.

@@

\item Users can generate U to select the element above the currently selected element,
or generate D to select the element below the selected element.
Whenever the selection is changed, 3. is performed.
If the depth of the newly selected element is different from the currently
selected element, siblings of the currently selected element will disappear.

\item When a newly selected element has children and the user performs no further action,
the first child of the selected elemented is newly selected and 3. is performed.
As a result, all the siblings of the newly selected element
(the first child of the currently selected elmeent) appear in the list.

@@

We show how {\ST} works, using a hierarchical data structure of
shops list in a shopping mall shown in Figure \ref{fig1}.
Rectangles with thick border represent categories, and
other rectangles represent individual shops.

@@

When the user generates D twice,
\tsf{Fresh grocery} category is selected (Figure \ref{fig6}).

@@

If the user keeps generating D, 
the list will change to Figure \ref{fig8},
without expanding the children of \tsf{Fresh grocery}.

If the use stops generating D at Figure \ref{fig6},
the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).

@@

When the user generates U here, \tsf{Fresh grocery} is selected,
and the shops under \tsf{Fresh grocery} disappears (Figure \ref{fig6}).
If the user generates U two more times, the display changes to the state
shown in Figure \ref{fig5},
and one more U will set the system to Figure \ref{fig4}.

@@

When the user generates D twice in Figure \ref{fig7},
\tsf{Clothing} is selected, and the category will be expanded (Figure \ref{fig8}).

@@

A prototype system was built in JavaScript and runs on modern browsers.
Huge list of of news articles, movies, anime films, musics, and e-books are listed in one browser window
and the content is displayed in another window.
Users can hit two arrow keys or use the PowerMate device for the navigation.

ここにスクリーンショット

\begin{figure}[H]
\centerline{\includegraphics[width=30mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
\caption{A PowerMate used for the prototype.}
\label{powermate}
\end{figure}

@@

4-way navigation are quite common for exploring hierarchical data structure,
and modern computer users have no problem using it.
Many mobile phones and PDAs are equipped with a jog dial with a push button,
where the dial is used for selecting an item from a list and 
the push button is used for moving to the next level.
PowerMate is equipped with a push button which can used for such purposes.
% As far as we know,
To the best of the authors' knowledge,
{\ST} is the only interaction method for exploring hierarchical data structure
with one rotating device.

Using a conventional hierarchical menu, children elements are displayed automatically
when the parent element is selected by a mouse.
The ``automatic expansion'' feature is {\ST}と同じ。

@@

LensBar\cite{Masui:1998:LVB:647341.721215}
is also a ZUI system for handling large hierarchical data,
but the same data structure used in LensBar can be used for {\ST}.
Users can use a pointing devices when it is appropriate,
and use two keys or a disk device when pointing devices is not available.

@@

No formal evaluation have been done yet, but {\ST} has been used in the authors'
living room for several months, and the author's family members are using it
everyday for watching anime films and listening to music.

Since the only thing a user can do with {\ST} is rotating the device,
a user can use the device and see what happens without thinking about
other interactions.
Using a disk device for data navigation might be a new experience for
most of the users, but the hard restriction of the usage seems to be a
good thing.
